% Document Type: LaTeX Article
% Purpose: This LaTeX document serves as a Curriculum Vitae (CV) for Aadarsha Gopala Reddy.
% It is structured to present academic qualifications, research experience, teaching roles,
% industry experience, skills, honors, presentations, leadership roles, and projects
% in a clear, organized, and professional manner. The CV utilizes a custom LaTeX style
% defined in 'reddy_cv.sty' for consistent formatting and layout.
%
% --- Preamble ---
% \documentclass[10pt, letterpaper]{article}
%   - Specifies the document class as 'article'.
%   - Sets the base font size to 10pt.
%   - Sets the paper size to 'letterpaper'.
%
% \usepackage{reddy_cv}
%   - Imports a custom LaTeX package named 'reddy_cv.sty'. This package is presumed
%     to define custom environments (e.g., `header`, `twocolentry`, `onecolentry`,
%     `highlightsforbulletentries`, `honorstwocolentry`), custom commands
%     (e.g., `\hrefWithoutArrow`, `\qrcode`, `\AND`), and custom spacing macros
%     (e.g., `\kernSpacing`, `\headerSpacing`, `\entrySpacing`, `\highlightSpacing`)
%     to achieve the specific layout and style of this CV.
%
% --- Document Body ---
% \begin{document} ... \end{document}
%   - This environment encloses the entire visible content of the CV.
%
% --- Header Section ---
% \begin{header} ... \end{header}
%   - A custom environment for the CV's header.
%   - It is internally structured using `minipage` environments to create a multi-column layout.
%   - Left column (0.65\textwidth):
%     - Displays the name "Aadarsha Gopala Reddy" in a large font size.
%     - Lists contact information: email and phone number.
%     - `\hrefWithoutArrow` is used for hyperlinking email and phone, likely a custom
%       command to style hyperlinks without the default box or arrow.
%     - `\kern \kernSpacing` and `\AND` are used for horizontal spacing and separation
%       of contact details.
%   - Middle column (0.16\textwidth, right-aligned):
%     - Displays the personal website URL, hyperlinked.
%   - Right column (0.10\textwidth, right-aligned):
%     - Displays a QR code (`\qrcode`) linking to the personal website.
%
% --- Spacing Elements ---
% - `\vspace{\headerSpacing}`, `\vspace{\entrySpacing}`, `\vspace{\highlightSpacing}`:
%   These commands insert vertical space of predefined lengths. The lengths
%   `\headerSpacing`, `\entrySpacing`, and `\highlightSpacing` are likely defined
%   in `reddy_cv.sty` to ensure consistent spacing between sections, entries,
%   and highlight blocks respectively.
%
% --- Main Sections ---
% The CV is organized into several standard sections using `\section{SECTION NAME}`.
%
% 1. \section{EDUCATION}
%    - Lists academic degrees, institutions, and relevant details.
%    - Uses `\begin{twocolentry}{Date Range}` to display the period of study alongside
%      the degree name and university.
%    - `\begin{onecolentry}` with `\begin{highlightsforbulletentries}` is used for
%      bulleted lists detailing GPA, coursework, and minors.
%
% 2. \section{RESEARCH EXPERIENCE}
%    - Details research projects, including titles (hyperlinked to repositories),
%      affiliations, and dates/contexts.
%    - `\mbox{}` is used to group project titles/links and affiliations.
%    - `\begin{twocolentry}{Date/Context}` specifies the timeframe or related course.
%    - `\begin{onecolentry}` with `\begin{highlightsforbulletentries}` lists key
%      contributions, methods used, and outcomes for each project.
%
% 3. \section{TEACHING EXPERIENCE}
%    - Describes roles and responsibilities in teaching or academic support.
%    - `\begin{twocolentry}{Date Range}` for the position and institution.
%    - `\begin{onecolentry}` with `\begin{highlightsforbulletentries}` for detailed responsibilities.
%
% 4. \section{INDUSTRY EXPERIENCE}
%    - Outlines professional roles, internships, and company affiliations.
%    - Structure is similar to Teaching Experience, using `twocolentry` for role/dates
%      and `onecolentry` with `highlightsforbulletentries` for accomplishments.
%
% 5. \section{SKILLS}
%    - Lists technical and non-technical skills categorized for clarity.
%    - Each category (e.g., Programming Languages, Frameworks & Libraries, Tools & Technologies,
%      Core Competencies, Languages) is presented within a `\begin{onecolentry}`.
%    - Skill categories are bolded, followed by a list of specific skills.
%
% 6. \section{HONORS}
%    - Enumerates awards, scholarships, and other academic distinctions.
%    - Uses a custom `\begin{honorstwocolentry}{Date/Year}` environment for each honor,
%      listing the date/year and the honor details (name and awarding institution).
%
% 7. \section{PRESENTATIONS}
%    - Lists academic or professional presentations given.
%    - Uses `\begin{twocolentry}{Date}` to display the date alongside the presentation
%      title and the event/venue.
%
% 8. \section{LEADERSHIP EXPERIENCE}
%    - Details leadership roles held in various organizations or student groups.
%    - Each entry typically includes the organization name and location, followed by
%      `\begin{twocolentry}{Date Range}` for the role and tenure, and
%      `\begin{onecolentry}` with `\begin{highlightsforbulletentries}` for
%      responsibilities and achievements.
%
% 9. \section{PROJECTS}
%    - Showcases significant academic or personal projects not covered under Research Experience.
%    - `\begin{twocolentry}{Date}` is used for the project title (often hyperlinked) and
%      the context (e.g., course, institution).
%    - `\begin{onecolentry}` with `\begin{highlightsforbulletentries}` describes the
%      project's objectives, technologies used, and key outcomes.
%
% --- General LaTeX Formatting and Commands Used ---
% - `\mbox{text}`: Ensures 'text' stays on a single line.
% - `\textbf{text}`: Formats 'text' in bold.
% - `\textit{text}`: Formats 'text' in italics.
% - `\kern \kernSpacing`: Inserts custom horizontal space. `\kernSpacing` is likely a
%   predefined length.
% - `\AND`: A custom macro, possibly for a separator symbol (e.g., "|") with spacing.
% - `\fontsize{size}{skip}\selectfont`: Sets font size and leading.
% - `\raggedright`, `\raggedleft`: Text alignment commands.
% - `\href{url}{text}`: Standard hyperlink command (though `\hrefWithoutArrow` is more common here).
%
% This CV template is well-structured, leveraging custom LaTeX capabilities for a
% professional and maintainable document.
\documentclass[10pt, letterpaper]{article}
\usepackage{reddy_cv}

\begin{document}

\begin{header}
    \begin{minipage}[t]{0.65\textwidth}
        \fontsize{20pt}{20pt}\selectfont \textbf{Aadarsha Gopala Reddy}\\
        \normalsize
        % \mbox{St. Louis, Missouri 63112 USA}%
        % \kern \kernSpacing%
        % \AND%
        % \kern \kernSpacing%
        \mbox{\hrefWithoutArrow{mailto:a.gopalareddy@wustl.edu}{a.gopalareddy@wustl.edu}}%
        \kern \kernSpacing%
        \AND%
        \kern \kernSpacing%
        \mbox{\hrefWithoutArrow{tel:+17408021776}{+1 (740) 802-1776}}%
        % \kern \kernSpacing%
        % \AND%
        % \kern \kernSpacing%
        % \mbox{\href{https://agopalareddy.github.io}{\raggedright agopalareddy.github.io}}%
    \end{minipage}
    \hfill
    \begin{minipage}[t]{0.15\textwidth}
        \raggedleft
        \href{https://agopalareddy.github.io}{agopalareddy.github.io}
    \end{minipage}
    \hfill
    \begin{minipage}[t]{0.11\textwidth}
        \raggedleft
        \qrcode{https://agopalareddy.github.io}
    \end{minipage}
\end{header}

\vspace{\headerSpacing}
\section{EDUCATION}

\begin{educationentry}{M.S. Computer Science}{Washington University in St. Louis, St. Louis, Missouri, USA}{Fall 2024 - *Spring 2026}
    \item \textbf{GPA:} 3.52/4.0
    \item \textbf{Coursework:}  Artificial Intelligence for Health, Neurobiology of Learning \& Memory, Advanced Neuroscience Research Methods, Computational Biology, Deep Learning, Systems Security, Software Development, and Introduction to Quantum Computing.
\end{educationentry}

\begin{educationentry}{B.A. Computer Science and Data Analytics}{Ohio Wesleyan University, Delaware, Ohio, USA}{Fall 2020 - Spring 2023}
    \item \textbf{Minor:} Economics
    \item \textbf{GPA:} 3.42/4.0
    \item \textbf{Coursework:} Computer Architecture, Theory of Computation, Algorithms, Big Data, Data Visualization, Data Analytics, Databases, Machine Learning, Artificial Intelligence, Applied Statistics.
\end{educationentry}

\vspace{\headerSpacing}
\section{RESEARCH EXPERIENCE}

\begin{researchentry}{\href{https://github.com/agopalareddy/CSE419A_Multimodal_Prediction_of_Alzheimers}{Multimodal Prediction of Alzheimer's Disease}}{Washington University in St. Louis}{St. Louis, Missouri, USA}{CSE 419A - Introduction to AI for Health}{Fall 2024}
    \item Developed a multimodal approach for early detection of Alzheimer's Disease using the OASIS-1 dataset.
    \item Implemented deep learning models (CNNs) using TensorFlow/Keras for MRI image analysis and machine learning techniques (XGBoost, Scikit-learn) for clinical data processing.
    \item Created a combined classifier leveraging both imaging and clinical data.
    \item Documented the project in NeurIPS format with comprehensive performance evaluation metrics and visualizations.
\end{researchentry}

\begin{researchentry}{\href{https://github.com/agopalareddy/DATA490}{Opinion Survey on Artificial Intelligence in the Workplace}}{Ohio Wesleyan University}{Delaware, Ohio, USA}{DATA 490 - Independent Study}{Spring 2023}
    \item Designed, fielded, and investigated a survey experiment on the impact of AI on 250 employees within each of four industries using survey data under Dr. Nicholas Dietrich's mentorship.
    \item Analyzed data using Tableau dashboards and R to identify trends and common opinions.
    \item Presented preliminary results on AI's positive impact on employee work at the OWU Spring Student Symposium.
\end{researchentry}

\begin{researchentry}{\href{https://github.com/agopalareddy/CS340Final-Connect4}{Connect 4 AI}}{Ohio Wesleyan University}{Delaware, Ohio, USA}{CS 340 - Artificial Intelligence}{Fall 2022}
    \item Developed a Connect 4 game in Java with a single-player mode against an AI opponent and a multiplayer mode for two human players.
    \item Used the alpha-beta pruning algorithm to create a challenging AI opponent that can test players of all skill levels.
\end{researchentry}

\begin{researchentry}{\href{https://github.com/agopalareddy/LostCities}{Artificial Intelligence in Modern Board Games - Lost Cities AI}}{Ohio Wesleyan University}{Delaware, Ohio, USA}{Summer Science Research Program}{Summer 2022}
    \item Developed a digital version of the Lost Cities card game using Java in 2 weeks under Dr. Sean McCulloch's mentorship.
    \item Implemented an intelligent agent that played the game against a human, winning 13 of 18 games in testing.
\end{researchentry}

\vspace{\headerSpacing}
\section{TEACHING EXPERIENCE}

\begin{experienceentry}{Computer Science Lab Assistant}{Ohio Wesleyan University}{Delaware, Ohio, USA}{Spring 2022 - Spring 2023}
    \item Tutored approximately ten students for over 6 hours per week, assisting with homework and exam preparation for introductory, intermediate, and advanced computer science coursework.
    \item Tested and graded assignments of around 35 students in introductory and intermediate computer science classes.
\end{experienceentry}

\vspace{\headerSpacing}
\section{INDUSTRY EXPERIENCE}

\begin{experienceentry}{Graduate Assistant with the Taylor Family Center for Student Success}{Washington University in St. Louis}{St. Louis, Missouri, USA}{Fall 2024 - Spring 2025}
    \item Led initiatives to enhance first gen/limited income student success, including program planning, data analysis, and communication.
    \item Coordinated key events, tracked student data, and contributed to assessment efforts for the department.
    \item Supported alumni engagement through newsletter development, database management, and other logistics.
\end{experienceentry}

\begin{experienceentry}{Data Analyst Intern}{Lab714}{Boca Raton, Florida, USA}{Summer 2023 - Summer 2024}
    \item Achieved a 20\% reduction in costs for clients through data-driven insights.
    \item Engineered a software using React and AWS to extract, organize, and analyze data from IoT devices.
\end{experienceentry}

\begin{experienceentry}{Media Center Assistant}{Ohio Wesleyan University}{Delaware, Ohio, USA}{Fall 2021 - Spring 2023}
    \item Set up and tore down audio-visual equipment, logged equipment movement using Sierra, and created appointments for use of spaces.
    \item Assisted with providing AV systems and support for events, ensuring successful setup and execution.
\end{experienceentry}

\vspace{\headerSpacing}
\section{SKILLS}

\begin{skillcategory}{Programming Languages}
    Java, C++, Python, R, JavaScript/TypeScript, PHP, C\#, SQL, Rust.
\end{skillcategory}

\begin{skillcategory}{Frameworks \& Libraries}
    TensorFlow, PyTorch, Scikit-learn, NumPy, Pandas, Node.js, Vue.js, React, Socket.IO, Gemini/OpenAI API.
\end{skillcategory}

\begin{skillcategory}{Tools \& Technologies}
    Git, Tableau, Power BI, MySQL, AWS, MongoDB, MySQL, Microsoft 365, Google Workspace.
\end{skillcategory}

\begin{skillcategory}{Core Competencies}
    Analytical Skills, Problem Solving, Critical Thinking, Communication, Team Collaboration, Leadership, Adaptability, Project Management.
\end{skillcategory}

\begin{skillcategory}{Languages}
    Proficient in English, Kannada, Telugu; Fundamental in Hindi.
\end{skillcategory}

\vspace{\headerSpacing}
\section{HONORS}

\begin{honorentry}{Spring 2022 \& Spring 2023}{\textbf{Dean's List}, Ohio Wesleyan University}
\end{honorentry}

\begin{honorentry}{Spring 2023}{\textbf{Mortar Board National College Senior Honor Society Membership}, Ohio Wesleyan University}
\end{honorentry}

\begin{honorentry}{Spring 2023}{\textbf{Golden Bishop Award}, Ohio Wesleyan University}
\end{honorentry}

\begin{honorentry}{Spring 2022}{\textbf{Florence Leas Sophomore Prize}, Ohio Wesleyan University}
\end{honorentry}

\begin{honorentry}{Spring 2022}{\textbf{First Place - 32nd Annual Spring Programming Contest}, Denison University}
\end{honorentry}

\begin{honorentry}{2020}{\textbf{International Baccalaureate Scholarship}, Ohio Wesleyan University}
\end{honorentry}

\begin{honorentry}{2020}{\textbf{Scholar}, Next Genius Scholarship Foundation}
\end{honorentry}

\vspace{\headerSpacing}
\section{PRESENTATIONS}

\begin{presentationentry}{Spring 2023}{Artificial Intelligence Opinion Survey}{Spring Student Symposium}{Ohio Wesleyan University}
\end{presentationentry}

\begin{presentationentry}{Fall 2022}{Artificial Intelligence in Modern Board Games}{Patricia Belt Conrades Summer Science Research Symposium}{Ohio Wesleyan University}
\end{presentationentry}

\vspace{\headerSpacing}
\section{LEADERSHIP EXPERIENCE}

\begin{leadershipentry}{Graduate and Professional Student Council (GPSC)}{Washington University in St. Louis, St. Louis, Missouri, USA}
    \begin{positionentry}{Vice President of the Graduate-Professional Council (GPC) Chamber}{Summer 2025 - Present}
        \item Actively support the GPC Co-President in fulfilling leadership responsibilities and advancing council goals for the Master's and Professional student body. As per the constitution, prepared to assume the duties and powers of the Co-President in their absence to ensure leadership continuity.
        \item Represent and advocate for GPC constituents' interests to university administration and faculty.
    \end{positionentry}
    \begin{positionentry}{McKelvey School of Engineering Representative, and member of the membership, Constitution, \& Outreach Committee}{Fall 2024 - Spring 2025}
        \item Co-authored the GPSC's constitution and spearheaded outreach initiatives that expanded membership.
        \item Advocated for the interests and concerns of McKelvey School of Engineering students.
    \end{positionentry}
\end{leadershipentry}

\begin{leadershipentry}{UMANG (Indian Graduate Student Association)}{Washington University in St. Louis, St. Louis, Missouri, USA}
    \begin{positionentry}{Treasurer}{Summer 2025 - Present}
        \item Managing club finances, including budgeting, expense tracking, and fundraising to ensure sustainable operations and successful event planning.
        \item Collaborating with members to organize cultural events and festivals, promoting cultural awareness and fostering community among Indian graduate students.
    \end{positionentry}
\end{leadershipentry}

\begin{leadershipentry}{HackWashU}{Washington University in St. Louis, St. Louis, Missouri, USA}
    \begin{positionentry}{Treasurer}{Fall 2024 - Present}
        \item Managing the club's finances, including budgeting and expense tracking, to ensure sustainable operations and successful event planning.
        \item Coordinating fundraising efforts and sponsorship outreach to support club activities and initiatives.
        \item Collaborating with club members to organize hackathons and coding events, fostering a culture of innovation and teamwork among participants.
    \end{positionentry}
\end{leadershipentry}

\begin{leadershipentry}{Association of Graduate Engineering Students (AGES)}{Washington University in St. Louis, St. Louis, Missouri, USA}
    \begin{positionentry}{Member}{Fall 2024 - Present}
        \item Organizing events and initiatives to foster community among graduate engineering students, enhancing networking and professional development opportunities.
    \end{positionentry}
\end{leadershipentry}

\needspace{5\baselineskip}
\begin{leadershipentry}{Hindu Student Council}{Ohio Wesleyan University, Delaware, Ohio, USA}
    \begin{positionentry}{Treasurer and Founding Member}{Spring 2023}
        \item Submitted formal budget requests and organized events to raise awareness of Hindu cultural heritage and provide youth leadership development and volunteer opportunities.
    \end{positionentry}
\end{leadershipentry}

\begin{leadershipentry}{Wesleyan Council on Student Affairs (Student Government)}{Ohio Wesleyan University, Delaware, Ohio, USA}
    \begin{positionentry}{Budget Committee Senator}{Fall 2022 - Spring 2023}
        \item Proposed, discussed, and decided bills for the senate and oversaw budget allocation of over \$350,000 each year to individuals, clubs, and organizations on campus.
        \item Awarded WCSA Best New Member Golden Bishop Award for making outstanding contributions to the council's missions, goals, and agenda.
    \end{positionentry}
\end{leadershipentry}

\begin{leadershipentry}{The Neurds (Neuroscience Club)}{Ohio Wesleyan University, Delaware, Ohio, USA}
    \begin{positionentry}{Member}{Fall 2022 - Spring 2023}
        \item Presented on AI at Brain Fair 2023 during Brain Awareness Week, bridging neuroscience and technology.
        \item Aided event planning and marketing for the club's educational and networking goals.
        \item Promoted neuroscience awareness and community service for intellectual and career development.
    \end{positionentry}
\end{leadershipentry}

\begin{leadershipentry}{Campus Programming Board}{Ohio Wesleyan University, Delaware, Ohio, USA}
    \begin{positionentry}{Vice President of Finance}{Spring 2022 - Fall 2022}
        \item Successfully planned, created, and implemented budgets totaling over \$86,000 each year for campus events.
        \item Initiated and led revamp of organization's governing documents, implementing efficient practices.
        \item Negotiated an additional \$10,000 per year with the Wesleyan Council on Student Affairs.
    \end{positionentry}

    \begin{positionentry}{Marketing Committee Member}{Fall 2020 - Spring 2023}
        \item Spearheaded social media campaigns and designed promotional materials to enhance student engagement and event visibility.
        \item Organized marketing initiatives, including posters, tabling events, and giveaways, to maximize student participation and attendance at events.
    \end{positionentry}
\end{leadershipentry}

\begin{leadershipentry}{Mathematics, Computer Science \& Data Analytics Student Board}{Ohio Wesleyan University, Delaware, Ohio, USA}
    \begin{positionentry}{Member}{Fall 2021 - Spring 2023}
        \item Analyzed faculty evaluations to provide actionable insights for departmental improvements.
        \item Gathered and synthesized student feedback on course offerings to recommend enhancements to the department.
    \end{positionentry}
\end{leadershipentry}

\begin{leadershipentry}{Horizons International}{Ohio Wesleyan University, Delaware, Ohio, USA}
    \begin{positionentry}{Marketing Committee Chair}{Fall 2021 - Fall 2022}
        \item Led social media campaigns, designed materials to boost international student event awareness and engagement.
        \item Organized marketing for cultural exchange, creating a welcoming environment for international students and fostering cross-cultural understanding within the university community.
    \end{positionentry}
\end{leadershipentry}

\vspace{\headerSpacing}
\section{PROJECTS}

\begin{projectentry}{\href{https://github.com/agopalareddy/CSE510A_Datacenter_Cooling}{Datacenter Cooling Optimization using Deep Reinforcement Learning}}{Washington University in St. Louis}{St. Louis, Missouri, USA}{Fall 2024}
    \item Implemented multiple deep reinforcement learning algorithms (DDQN, PPO, SAC) integrated with EnergyPlus simulations to optimize datacenter cooling systems.
    \item Achieved 35.8\% energy efficiency improvement over baseline using DDQN, addressing the underserved small to mid-sized datacenter market.
    \item Created a comprehensive framework integrating building energy simulation with reinforcement learning for dynamic thermal management.
\end{projectentry}

\begin{projectentry}{\href{https://github.com/agopalareddy/CSE503S_Interactive_Storybook}{Interactive Storybook}}{Washington University in St. Louis}{St. Louis, Missouri, USA}{Fall 2024}
    \item Developed an interactive storytelling application using Vue.js, Node.js, and MongoDB with AI-powered content generation, enabling users to create branching narrative stories.
    \item Implemented OpenAI API integration for dynamic story text and contextual image generation based on user choices.
    \item Created a visual path tracking interface to help users navigate complex branching narratives and story progression.
\end{projectentry}
\begin{projectentry}{\href{https://github.com/agopalareddy/CSE503S_Chat_App}{Socket.IO Multi-Room Chat Application}}{Washington University in St. Louis}{St. Louis, Missouri, USA}{Fall 2024}
    \item Developed a feature-rich multi-room chat application using Node.js and Socket.IO with password-protected rooms, private messaging, and user moderation capabilities.
    \item Implemented room management features including creator privileges, user tracking, and persistent nickname storage.
    \item Created real-time bidirectional event-based communication with responsive design for optimal user experience.
\end{projectentry}

\needspace{7\baselineskip}
\begin{projectentry}{\href{https://github.com/agopalareddy/CSE503S_PHP_Calendar_App}{PHP Calendar Application}}{Washington University in St. Louis}{St. Louis, Missouri, USA}{Fall 2024}
    \item Developed a feature-rich personal calendar and event management web application using PHP, MySQL, HTML5, CSS3, and JavaScript.
    \item Implemented secure user authentication, CSRF protection, SQL injection prevention, and input sanitization.
    \item Created an interactive calendar interface with comprehensive event management capabilities for creation, editing, and tracking.
\end{projectentry}

\begin{projectentry}{\href{https://github.com/agopalareddy/AIPS}{Parkinson's Disease AI Diagnosis Software}}{MITxSureStart FutureMakers Create-a-Thon Program}{Remote}{Summer 2022}
    \item Developed AIParkinScan software for Parkinson's diagnosis using neural networks, spectrograms, and the Random Forest algorithm trained on audio and image data.
\end{projectentry}

\end{document}
